Improving schedulability rate of EDF when taking into account the preemption cost in uniprocessor periodic systems

### 2013-10-07 python-simulation/paper-paedf/paper-paedf.tex
now with some figs

        Once a previously preempted job is chosen for computation by the scheduling policy, it enters an uninterruptible preemption recovery period.\\

        [figure]\\

@@

        [figure]\\

@@

        [figure]\\

>>>>

        Once a previously preempted job is chosen for computation by the scheduling policy, it enters an uninterruptible preemption recovery period, as seen in Fig.~\ref{fig:prp}.\\

        \begin{figure}[h]
        \begin{center}
            \includegraphics[width=\textwidth]{figs/atomicpreemption_example.png}
            \caption{Schedule of a system with $\alpha=2$. At t $t=6$, the preemption recovery period is not interrupted even though a job with higher priority is activated}
            \label{fig:prp}
        \end{center}
        \end{figure}

@@

        \begin{figure}[h]
        \begin{center}
            \includegraphics{figs/edfNonOptimal_EDF.png}
            \caption{A system scheduled by EDF where a deadline is missed}
            \label{fig:edfnonoptimal_edf}
        \end{center}
        \end{figure}

@@

        \begin{figure}[h]
        \begin{center}
            \includegraphics{figs/edfNonOptimal_PALLF.png}
            \caption{The system of Fig.~\ref{fig:edfnonoptimal_edf} with a different schedule in which no deadline is missed}
            \label{fig:edfnonoptimal_pallf}
        \end{center}
        \end{figure}
